EinsteinPy: Python for General Relativity\footnote{Released on January, 8th, 2018}

### 2019-07-10 paper.tex
Add authors till now

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

>>>>

\author[0000-0002-2268-9772]{Sofía Ortín Vela}
\affil{Department of Theoretical Physics, University of Zaragoza \\
Zaragoza, Spain}

\author[0000-0001-8530-7252]{Jialin Ma}
\affil{Georgia Institute of Technology, GA 30332, USA}

\author[0000-0001-8530-7252]{Jialin Ma}
\affil{Georgia Institute of Technology, GA 30332, USA}

\author[0000-0001-7234-6148]{Varun Singh}
\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
Mandi, Himachal Pradesh, 175005, India}

\author[0000-0002-1900-3338]{Shilpi Jain}
\affiliation{Department of Earth Sciences, Indian Institute of Technology Roorkee, India}

\author[0000-0002-7179-3795]{Alpesh Jamgade}
\affiliation{Department of Mathematics, Bharath Institute of Higher Education and Research, Chennai, India}

\author[0000-0002-5198-9010]{Manvi Gupta}
\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
Mandi, Himachal Pradesh, 175005, India}

\author{Tushar Tyagi}
\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
Mandi, Himachal Pradesh, 175005, India}

\author[0000-0003-1838-8368]{Tanmay Rustagi}
\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
Mandi, Himachal Pradesh, 175005, India}

\author[0000-0002-0757-2883]{Abhijeet Manhas}
\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
Mandi, Himachal Pradesh, 175005, India}

\author[0000-0001-5558-9447]{Raphael Reyna}
\affiliation{California State Polytechnic University, Pomona}

\author[0000-0001-8302-1584]{Sashank Mishra}
\affiliation{Department of Information Technology, Indian Institute of Information Technology Allahabad}
\collaboration{(EinsteinPy Package Contributors)}
%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.
